Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-18 sas2015/content/impl.tex
squeezing

In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
an IFDS solution as:
  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
%is converted to an IFDS result as follows:
%\begin{equation}\label{eq:transEqDef}
  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
%\end{equation}
%
%\otodo{I don't understand this comment. What does it mean?}
%
In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, an IDE solution $\rho$ computed using
$\transCC_S$ is converted to an IFDS solution as
\begin{equation}
	\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.\label{eq:transCcDef}
\end{equation}

@@

The equivalence analysis is there for two reasons: 
(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis\footnote{
We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
}.

The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}. In the table, $N^*_r$ is the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
\input{tables/runstats}

>>>>

In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
an IFDS solution as:
  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
%is converted to an IFDS result as follows:
%\begin{equation}\label{eq:transEqDef}
  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
%\end{equation}
%
%\otodo{I don't understand this comment. What does it mean?}
%
In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, an IDE solution $\rho$ computed using
$\transCC_S$ is converted to an IFDS solution as
\vspace{-.4cm}
\begin{equation}
	\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.\label{eq:transCcDef}
\end{equation}

@@

The equivalence analysis is there for two reasons: 
(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis%\footnote{
We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
%}
.

The running times $t_\Subset$ of the correlated-calls and $t_\equiv$ equivalence analyses are shown in Table~\ref{tab:runtimes}. In the table, $N^*_r$ is the number of reachable nodes in the control-flow supergraph, and $N^\#_r$ the number of reachable nodes in the exploded supergraph.
\vspace{-.7cm}
\input{tables/runstats}
